---
title: "india_failure_ml_h20ai"
author: "avanvalken"
date: "4/27/2022"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    theme: "flatly"
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
suppressPackageStartupMessages({
  library(SummarizedExperiment)
  library(edgeR)
  library(sva)
  library(SingleCellExperiment)
  library(singleCellTK)
  library(DESeq2)
  library(TBSignatureProfiler)
  library(DT)
  library(enrichR)
  library(Rtsne)
  library(umap)
  library(ggplot2)
  library(ComplexHeatmap)
  library(tidyverse)
  library(knitr)
  library(kableExtra)
  library(h2o)
  
  
})

knitr::opts_chunk$set(cache = TRUE)
knitr::opts_chunk$set(echo = FALSE)
##knitr::opts_chunk$set(dev = "svg", dpi = 300)

```


# Load data
```{r}
indata <- readRDS("data_processed/tx_failure_batchcorrected.RDS")
indata <- indata[,colData(indata)$visit=="Baseline"] # focus on baseline
dim(indata)
```


## h2o.ai
```{r}
#library(h2o)
# Start the H2O cluster (locally)
h2o.init()

# make h20.ai object
mat_h2o <- as.h2o(bl_mat) 
predictors <- colnames(mat_h2o[,-length(mat_h2o)])
y <- 'subjtype'

#mat_splits <- h2o.splitFrame(data = mat_h2o, 
     #                         ratios = 0.8, seed = 1)
train <- as.h2o(bl_mat[train_subjid,])
test <- as.h2o(bl_mat[test_subjid,])


```

## H2O Kmeans
```{r, eval=FALSE}
kmeans_model <- h2o.kmeans(training_frame = train, 
                           x = predictors, k = 3,
                           seed = 1)
h2o.centers(kmeans_model)
```


```{r, eval=F, echo=F}
mat_automl <- h2o.automl(x = predictors, y = y, 
                          training_frame = train, 
                          max_runtime_secs = 0,
                          exclude_algos="DeepLearning",
                          max_models=15,
                          seed=1919) # , 
                          #validation_frame = valid) must have 200 weighted rows?
```



## H2O AutoML leaderboard
```{r, eval=T}

lb <- h2o.get_leaderboard(mat_automl)
head(lb)
```

## H2O get leader
```{r}
m <- mat_automl@leader
m1 <- h2o.getModel("DRF_1_AutoML_1_20220511_134727")
m2 <- h2o.getModel("XRT_1_AutoML_1_20220511_134727")  

```

```{r}
h2o.varimp_plot(m)

 

m0_gbm <-  as.character(as.data.frame(h2o.varimp(m))[1:4,"variable"])
#names(m0_gbm) <- "m0_gbm"

m1_drf <- as.character(as.data.frame(h2o.varimp(h2o.getModel("DRF_1_AutoML_1_20220511_134727")))[1:14,"variable"])
#names(m1_drf) <- "m1_drf"

m2_xrt <- as.character(as.data.frame(h2o.varimp(h2o.getModel("XRT_1_AutoML_1_20220511_134727")))[1:16,"variable"])
#names(m2_xrt) <- "m2_xrt"


#View(as.data.frame(h2o.varimp(m)))
#"RNU6-11P", "SCYL3")

m3 <- as.character(unique(unlist(c(m0_gbm, m1_drf, m2_xrt))))
```




## Test the model with TBSignatureProfiler
```{r}
indata_base = indata[,colData(indata)$visit=="Baseline"]
indata_m2 = indata[,colData(indata)$visit == "Month 2"]


assay <- "log_cpm"
samp_tbsignatures <- TBsignatures


samp_tbsignatures$'VanValkenburg_FAIL_4' <- c("MSLN", "NHSL2", "LRRFIP1", "SLC6A6")
# samp_tbsignatures$'m1_drf' <- c("PBLD", 
#                                 "PLAGL1", 
#                                 "MSLN", 
#                                 "NHSL2", 
#                                 "TRBV5-1", 
#                                 "KIF1B", 
#                                 "H2BC20P", 
#                                 "HK2P1", 
#                                 "SSH1", 
#                                 "AC007686.3",
#                                 "EP300",
#                                 "AC024587.1",
#                                 "PRSS51", 
#                                 "TRAPPC10" )
samp_tbsignatures$'VanValkenburg_FAIL_14' <- c("STAT3",
                               "PLEKHM3",
                               "LRRFIP1",
                               #"AC009974.2",
                               "RREB1",
                               "RNASEL",
                               "SSH1",
                               "HELZ" ,
                               #"PTGIS",
                               "AC003681.1",
                               "PLEK",
                               "ANKRD28",
                               "KIF13A",
                               "RAB11FIP1P1",
                               "IDS",
                               "ANO6")
#samp_tbsignatures$'m3' <- m3

samp_tbsignatures$Chendi_HIV_2 <- NULL
#samp_tbsignatures$Kulkarni_HIV_2 <- NULL
#samp_tbsignatures$Sloot_HIV_2 <- NULL
#samp_tbsignatures$Suliman_RISK_2 <- NULL

test_indata <- indata_base[,which(colnames(indata_base) %in% test_subjid)]

train_indata <- indata_base[,which(colnames(indata_base) %in% train_subjid)]


gsva_res <- runTBsigProfiler(test_indata,
                             useAssay = assay,
                             algorithm = "GSVA",
                             signatures = samp_tbsignatures)

ssgsea_res <- runTBsigProfiler(test_indata,
                             useAssay = assay,
                             algorithm = "ssGSEA",
                             signatures = samp_tbsignatures)

plage_res <- runTBsigProfiler(test_indata,
                             useAssay = assay,
                             algorithm = "PLAGE",
                             signatures = samp_tbsignatures)

# gsva_res <- runTBsigProfiler(train_indata,
#                              useAssay = assay, 
#                              algorithm = "GSVA",
#                              signatures = samp_tbsignatures)
# 
# ssgsea_res <- runTBsigProfiler(train_indata,
#                              useAssay = assay, 
#                              algorithm = "ssGSEA",
#                              signatures = samp_tbsignatures)
# 
# plage_res <- runTBsigProfiler(train_indata,
#                              useAssay = assay,
#                              algorithm = "PLAGE",
#                              signatures = samp_tbsignatures)

```



#### AUC Table
```{r, message = FALSE}
set.seed(0)
d <- tableAUC(plage_res,
         annotationColName = "subjtype",
         signatureColNames = names(samp_tbsignatures),
         num.boot = 100,
         pb.show = FALSE,
         output="data.frame")
```









### ssGSEA {.tabset}

#### Heatmap

```{r subssgsea_a_TBsigs}
signatureHeatmap(ssgsea_res, name="ssGSEA", signatureColNames = names(samp_tbsignatures),
                 annotationColNames = c("subjtype"),
                 showColumnNames = FALSE, scale = TRUE,
                 split_heatmap='none')
```

#### Boxplot

```{r boxssgsea_TBsigs}
signatureBoxplot(ssgsea_res, name="ssGSEA", signatureColNames = names(samp_tbsignatures),
                 annotationColName = c("subjtype"), scale = TRUE) #rotateLabels = TRUE,
```

#### Boxplots Single {.tabset}

```{r , results="asis"}
for (i in names(samp_tbsignatures)){

  cat("#####", i, "\n")

  print(signatureBoxplot(ssgsea_res, name=i, signatureColNames = i,
                 annotationColName = c("subjtype"), rotateLabels = T))

  cat("\n\n")
}

```

#### Signature plots {.tabset}
```{r genes_ssgsea_TBsigs, results="asis"}
for (i in names(samp_tbsignatures)){

  cat("#####", i, "\n")

  signatureGeneHeatmap(ssgsea_res, useAssay="log_cpm",
                     samp_tbsignatures[[i]],
                     name = i, signatureColNames = NULL,
                     annotationColNames = c("subjtype",i),
                     showColumnNames = FALSE, 
                     column_order =  NULL)

  cat("\n\n")
}

```


#### AUC Table
```{r, message = FALSE}
set.seed(0)
tableAUC(ssgsea_res,
         annotationColName = "subjtype",
         signatureColNames = names(samp_tbsignatures),
         num.boot = 100,
         pb.show = FALSE)
```

#### AUC Boxplots {.tabset}
```{r, message = FALSE}
set.seed(0)
compareBoxplots(ssgsea_res, annotationColName = "subjtype",
                signatureColNames = names(samp_tbsignatures),
                pb.show = FALSE, fill.col = "blue",
                rotateLabels = TRUE)
```

#### ROC plots
```{r, message = FALSE, fig.height = 9, fig.width = 12}
signatureROCplot_CI(inputData = ssgsea_res,
                   signatureColNames = names(samp_tbsignatures),
                   annotationColName = "subjtype")

```

#### Separate ROC plots  {.tabset}

```{r, results = 'asis', message = FALSE}
for (i in names(samp_tbsignatures)){

  cat("#####", i, "\n")

  print(signatureROCplot(inputData = ssgsea_res,
                   signatureColNames = i,
                   annotationColName = "subjtype",
                   name = paste("ROC plot,", i, sep = " ")))

  cat("\n\n")
}
```


### PLAGE {.tabset}


#### Heatmap

```{r plage_TBsigs}
signatureHeatmap(plage_res, name="PLAGE", signatureColNames = names(samp_tbsignatures),
                 annotationColNames = c("subjtype"),
                 showColumnNames = FALSE,
                 split_heatmap='none')
```


#### Boxplot

```{r boxplage_TBsigs}
signatureBoxplot(plage_res, name="PLAGE", signatureColNames = names(samp_tbsignatures),
                 annotationColName = c("subjtype"))# , rotateLabels = TRUE)
```

#### Boxplots Single {.tabset}

```{r , results="asis"}
for (i in names(samp_tbsignatures)){

  cat("#####", i, "\n")

  print(signatureBoxplot(plage_res,
                         name=i, 
                         signatureColNames = i,
                         annotationColName = c("subjtype"),   
                         ##violinPlot = TRUE,
                         rotateLabels = T))

  cat("\n\n")
}

```



#### AUC Table ssGSEA
```{r, message = FALSE}
set.seed(0)


bl_test_AUC <- tableAUC(ssgsea_res,
         annotationColName = "subjtype",
         signatureColNames = names(samp_tbsignatures),
         num.boot = 100,
         pb.show = FALSE,
         output = "data.frame")
View(bl_test_AUC)
#write.csv(bl_test_AUC, "bl_test_AUC_ssgsea.csv")
```

#### AUC Table PLAGE
```{r, message = FALSE}
set.seed(0)
bl_test_AUC_plage <- tableAUC(plage_res,
         annotationColName = "subjtype",
         signatureColNames = names(samp_tbsignatures),
         num.boot = 100,
         pb.show = TRUE,
         output = "data.frame")
View(bl_test_AUC_plage)
#write.csv(bl_test_AUC_plage, "bl_test_AUC_plage.csv", append=FALSE)
```

#### ROC plots (ind)
```{r}
for (i in names(samp_tbsignatures)){

  cat("#####", i, "\n")

  print(signatureROCplot(inputData = plage_res,
                   signatureColNames = i,
                   annotationColName = "subjtype",
                   name = paste("ROC plot,", i, sep = " ")))

  cat("\n\n")
}
```

#### Boxplot ssGSEA

```{r}

select_tbsignatures <- list(samp_tbsignatures$VanValkenburg_FAIL_14,
                      samp_tbsignatures$Anderson_42, 
                      samp_tbsignatures$Esmail_203, 
                      samp_tbsignatures$Tornheim_71,
                      samp_tbsignatures$Tornheim_RES_25,
                      samp_tbsignatures$VanValkenburg_FAIL_4, 
                      samp_tbsignatures$Leong_RISK_29,
                      samp_tbsignatures$Thompson_FAIL_13,
                      samp_tbsignatures$Thompson_RES_5,
                      samp_tbsignatures$Maertzdorf_OD_100, 
                      samp_tbsignatures$Jacobsen_3,
                      samp_tbsignatures$Jenum_8)

names(select_tbsignatures) <- c("VanValkenburg_FAIL_14",
                      "Anderson_42", 
                      "Esmail_203", 
                      "Tornheim_71",
                      "Tornheim_RES_25",
                      "VanValkenburg_FAIL_4", 
                      "Leong_RISK_29",
                      "Thompson_FAIL_13",
                      "Thompson_RES_5",
                      "Maertzdorf_OD_100", 
                      "Jacobsen_3",
                      "Jenum_8")


#svg("tbfail_ssgsea_boxplot_selectsig.svg", pointsize = 8)
signatureBoxplot(ssgsea_res, name="ssGSEA", signatureColNames = names(select_tbsignatures),
                 annotationColName = c("subjtype"))# , rotateLabels = TRUE)
#dev.off()
```

#### Boxplot PLAGE
```{r}
#svg("tbfail_plage_boxplot_selectsig.svg", pointsize = 8)
signatureBoxplot(plage_res, name="PLAGE", signatureColNames = names(select_tbsignatures),
                 annotationColName = c("subjtype"))# , rotateLabels = TRUE)
#dev.off()
```


#### Heatmap of signature
```{r}
#png("tbfail_VanValkenburg_FAIL_14_train_plage_heatmap.png", pointsize = 8)
signatureGeneHeatmap(plage_res, useAssay="log_cpm",
                     samp_tbsignatures[["VanValkenburg_FAIL_14"]],
                     name = "VanValkenburg_FAIL_14_train_plage", signatureColNames = NULL,
                     annotationColNames = c("subjtype", "VanValkenburg_FAIL_14"),
                     showColumnNames = FALSE)
#dev.off()
```

#### Heatmap of m0_gbm signature
```{r}
#svg("VanValkenburg_FAIL_4_test_plage_heatmap.svg", pointsize = 8)
signatureGeneHeatmap(plage_res, useAssay="log_cpm",
                     samp_tbsignatures[["VanValkenburg_FAIL_4"]],
                     name = "VanValkenburg_FAIL_4_train_plage", signatureColNames = NULL,
                     annotationColNames = c("subjtype", "VanValkenburg_FAIL_4"),
                     showColumnNames = FALSE)
#dev.off()
```

# TBSignatureProfiler M2
```{r}
assay <- "log_cpm"
# samp_tbsignatures <- TBsignatures
# 
# 
# samp_tbsignatures$'m0_gbm' <- c("MSLN", "NHSL2", "LRRFIP1", "SLC6A6")
# samp_tbsignatures$'m1_drf' <- c("PBLD",
#                                 "PLAGL1",
#                                 "MSLN",
#                                 "NHSL2",
#                                 "TRBV5-1",
#                                 "KIF1B",
#                                 "H2BC20P",
#                                 "HK2P1",
#                                 "SSH1",
#                                 "AC007686.3",
#                                 "EP300",
#                                 "AC024587.1",
#                                 "PRSS51",
#                                 "TRAPPC10" )
# samp_tbsignatures$'m2_xrt' <- c("STAT3",
#                                "PLEKHM3",
#                                "LRRFIP1",
#                                "AC009974.2",
#                                "RREB1",
#                                "RNASEL",
#                                "SSH1",
#                                "HELZ" ,
#                                "PTGIS",
#                                "AC003681.1",
#                                "PLEK",
#                                "ANKRD28",
#                                "KIF13A",
#                                "RAB11FIP1P1",
#                                "IDS",
#                                "ANO6")
# 
# samp_tbsignatures$Chendi_HIV_2 <- NULL
# 





gsva_res <- runTBsigProfiler(indata_m2,
                             useAssay = assay, 
                             algorithm = "GSVA",
                             signatures = samp_tbsignatures)

ssgsea_res <- runTBsigProfiler(indata_m2,
                             useAssay = assay, 
                             algorithm = "ssGSEA",
                             signatures = samp_tbsignatures)

plage_res <- runTBsigProfiler(indata_m2,
                             useAssay = assay, 
                             algorithm = "PLAGE",
                             signatures = samp_tbsignatures)



```



#### AUC Table
```{r, message = FALSE}
set.seed(0)
tableAUC(gsva_res,
         annotationColName = "subjtype",
         signatureColNames = names(samp_tbsignatures),
         num.boot = 100,
         pb.show = FALSE)
```

#### AUC Table
```{r, message = FALSE}
set.seed(0)
x <- tableAUC(ssgsea_res,
         annotationColName = "subjtype",
         signatureColNames = names(samp_tbsignatures),
         num.boot = 100,
         pb.show = FALSE,
         output = "data.frame")
View(x)
#write.csv(x, "m2_test_AUC_ssgsea.csv")
```

#### AUC Table
```{r, message = FALSE}
set.seed(0)
x <- tableAUC(plage_res,
         annotationColName = "subjtype",
         signatureColNames = names(samp_tbsignatures),
         num.boot = 100,
         pb.show = FALSE,
         output = "data.frame")
View(x)
#write.csv(x, "m2_test_AUC_plage.csv")
```

#### ROC plots (ind)
```{r}

for (i in names(samp_tbsignatures)){

  cat("#####", i, "\n")

  print(signatureROCplot(inputData = plage_res,
                   signatureColNames = i ,
                   annotationColName = "subjtype",
                   name = paste("ROC plot,", i, sep = " ")))

  cat("\n\n")
}

svg("FAIL4_roc_plage_m2.svg")
signatureROCplot(inputData = plage_res,
                   signatureColNames = "VanValkenburg_FAIL_4" ,
                   annotationColName = "subjtype",
                   name = paste("ROC plot,", "VanValkenburg_FAIL_4", sep = " "))
dev.off()

svg("FAIL14_roc_plage_m2.svg")
signatureROCplot(inputData = plage_res,
                   signatureColNames = "VanValkenburg_FAIL_14" ,
                   annotationColName = "subjtype",
                   name = paste("ROC plot,", "VanValkenburg_FAIL_14", sep = " "))
dev.off()

```

#### Boxplot ssGSEA

```{r}



#svg("tb_fail_boxplot_ssgsea_m2.svg")
signatureBoxplot(ssgsea_res, name="ssGSEA", signatureColNames = names(select_tbsignatures),
                 annotationColName = c("subjtype"))# , rotateLabels = TRUE)
#dev.off()
```

#### Boxplot PLAGE
```{r}
png("tb_fail_boxplot_plage_m2.png")
signatureBoxplot(plage_res, name="PLAGE", signatureColNames = names(select_tbsignatures),
                 annotationColName = c("subjtype"))# , rotateLabels = TRUE)
dev.off()
```


#### Heatmap of signature
```{r}
png("tbfail_m2xrt_ssgsea_heatmap_m2.png", pointsize = 8)
signatureGeneHeatmap(ssgsea_res, useAssay="log_cpm",
                     samp_tbsignatures[["m2_xrt"]],
                     name = "m2_xrt", signatureColNames = NULL,
                     annotationColNames = c("subjtype", "m2_xrt"),
                     showColumnNames = FALSE)
dev.off()
```

```{r}
#png("tbfail_m0gbm_plage_heatmap_m2.png", pointsize = 8)
signatureGeneHeatmap(plage_res, useAssay="log_cpm",
                     samp_tbsignatures[["m0_gbm"]],
                     name = "m0_gbm", signatureColNames = NULL,
                     annotationColNames = c("subjtype", "m0_gbm"),
                     showColumnNames = FALSE)
#dev.off()
```



# Session Info
```{r}
sessionInfo()

```










